### 2016-06-29 publications/Journal/4a-allocation.tex
Save some space by putting figures next to each other

   \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PholdTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
   \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PholdTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

@@

\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth,  height=6cm, keepaspectratio]{fig/pholdtreed1n3t5000c4BFS.eps}
    \caption{Visualization of PholdTree (d=1,n=3,t=5000) parallel simulation with breadth first allocation and 4 kernels.}
    \label{fig:pholdtree_visualize_parBFS}
\end{figure}
\begin{figure}
    \center
    \includegraphics[width=\plotfraction\columnwidth,  height=6cm, keepaspectratio]{fig/pholdtreed1n3t5000c4DFS.eps}
    \caption{Visualization of PholdTree (d=1,n=3,t=5000) parallel simulation with depth first allocation and 4 kernels.}
    \label{fig:pholdtree_visualize_parDFS}
\end{figure}

>>>>

   \includegraphics[width=\textwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PholdTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
   \includegraphics[width=\textwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PholdTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

@@

\begin{figure}
    \center
    \begin{minipage}{0.45\textwidth}
            \center
            \includegraphics[width=\textwidth]{fig/pholdtreed1n3t5000c4BFS.eps}
            \caption{Visualization of a PholdTree simulation with breadth first allocation and 4 kernels.}
            \label{fig:pholdtree_visualize_parBFS}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
            \center
            \includegraphics[width=\textwidth]{fig/pholdtreed1n3t5000c4DFS.eps}
            \caption{Visualization of a PholdTree simulation with depth first allocation and 4 kernels.}
            \label{fig:pholdtree_visualize_parDFS}
    \end{minipage}
\end{figure}
